\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Example Project for Econ5970}
\author{Sloan C. Stinnett}
\date{January 2019}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Interest in Economics and Data Science}
\subsection{Economics}
My interest in economics is mainly centered on the micro-level. I am especially interested in how people make economics decisions in areas where economic value and ethical decision making collide. I am especially interested in market failures and the pricing of goods with very low price elasticity of demand. 
\subsection{Data Science}
Data science is the backbone of empirical economics, and really engaging in any research that relies on large sets of data. I see it as an important skill that will assist both with career goals and with structuring my own methods of looking into topics I find interesting.
\subsection{Project Ideas}
No topic for the final project has jumped out at me yet. I am looking at the later parts of the course for something that seems particularly interesting. 
\subsection{Goals for Class}
My goal for this class is primarily the development of a core of skills in programming and data science that I can build on with further study into the areas that catch my interest or that I feel seem to be the most important to improving my ability to do the kind of analytical work that I am interested in. 
\subsection{Goals After Graduation}
My plan for after graduation is bifurcated. I plan to apply to law school, if I am accepted into a top 20 law program with a good scholarship package than I plan to pursue law degree specializing in corporate law. If I don't get a satisfactory offer for law school than I plan to look for a job as an economic analyst.  
\equation{Equation}
$$ a^2+b^2=c^2 $$
\end{document}
